Analysis of the Anomalous Doppler Effect from Quantum Theory to Classical Dynamics Simulations

### 2025-06-17 paper modification/CPB-tex-template/CPB Template-LaTeX/paper_v3.tex
new materials

%=================================================================================================%
% This is a template designed for Chin. Phys. B (Dated 12 November 2014)
% Only one step to compile: PDFTeXify
%=================================================================================================%
\documentclass{cpbtex3}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{authblk}
%\usepackage[backend=biber]{biblatex}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{titlesec}      % For customizing section titles
% ===== 1. Small font for affiliations =====
\renewcommand{\Affilfont}{\small} % Set affiliation font size to small

@@

%\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{etoolbox}
\usepackage{microtype} 
\usepackage{caption}
\usepackage{hyperref}
\captionsetup[figure]{labelfont=bf, name=Fig., labelsep=period}
\bibliographystyle{cpb-num}

@@

\begin{abstract}
A quantum model incorporating angular momentum conservation is developed to analyze the Normal and Anomalous Doppler Effects, demonstrating that the resonance condition is strongly influenced by the angular momentum of the wave. The resonance condition involving wave angular momentum is examined numerically, and the energy exchange ratio between the electron's parallel and gyro-kinetic motion during resonance with the electromagnetic wave is simulated, exhibiting strong agreement with quantum theoretical predictions.
\end{abstract}

@@

\section{Introduction}
The Anomalous Doppler Effect (ADE) \cite{tamm1959general,frank1960optics,ginzburg1960certain,shustin1971transformation}, in which the observed frequency shift behaves contrary to the conventional Doppler Effect under specific conditions, was first theoretically predicted by Soviet physicist Vitaly L. Ginzburg \cite{ginzburg1946radiation}. This phenomenon arises when a system moves with a velocity exceeding the phase velocity of light in the medium, transferring its translational kinetic energy into internal energy while emitting radiation. A notable example, discussed by Frank in his 1958 Nobel lecture \cite{frank1960optics}, shows that radiation emission does not occur through the typical transition from an excited state to a lower energy state. Instead, it proceeds from a lower to a higher energy state, powered by the system's translational kinetic energy. This counterintuitive prediction has attracted considerable attention and has inspired extensive research \cite{nezlin1976negative,santini1984anomalous,kho1988slow,wang2016multi,guo2018control,liu2018role,shi2018superlight,filatov2021role}.

@@

The remainder of this paper is organized as follows. Section~\ref{Quantum}~~~ develops the quantum theoretical framework incorporating angular momentum conservation. Section~\ref{sec:level3}~~~ presents our numerical approach, detailing the simulation setup, analyzing the time evolution of electron velocity and kinetic energy, investigating the resonant conditions with wave angular momentum, and examining the energy transfer ratio and polarization characteristics. Section~\ref{sec:Discussion}~~~ provides a comprehensive discussion of the key findings and their physical implications. Finally, Section~\ref{sec:Conclusion}~~~ summarizes the principal conclusions and outlines potential directions for future research.

\section{Quantum analysis of ADE}\label{Quantum}
%We begin with the quantum theory proposed by V.L. Ginzburg\cite{ginzburg2005radiation}based on the energy-momentum conservation, and then incorporate  angular momentum conservation to illustrate the relationship of wave’s angular momentum and Landau level n under the resonant condition $\omega = \vec{k}\cdot \vec{v}+m \omega_{ce}$, where $\omega$ is wave’s angular frequency, $\vec{k}$ represents the wave vector,  $\vec{v}$ means the velocity of electron and $ \omega_{ce}$ is the electron cyclotron angular frequency in static magnetic field, $ m =0,±1,±2,…  $is the quantum number of the Landau levels\cite{coppi1976slide}.

@@

The $z$-component of the orbital angular momentum operator can be expressed in spherical coordinates as:
\begin{equation}
\hat{L}_z = -i\hbar\frac{\partial}{\partial\phi}  \label{eq:Lz}
\end{equation}
Combining Eq.~(\ref{eq:psi}) with Eq.~(\ref{eq:Lz}), we have 
\begin{equation}
-i\hbar \frac{\partial}{\partial \phi} \Psi = (p_\phi - eA_\phi) r \Psi
\end{equation}
As a result, the eigenvalue of  $L_z $can be expressed as
\begin{equation}
L_z = (p_\phi - e A_\phi) r  \label{eq:Lz_2}
\end{equation}
With \( p_\phi = \gamma m_e v_\perp \), \( A_\phi = \dfrac{r B_0}{2} \), and \( r = \dfrac{\gamma m_0 v_\perp}{B_0 e} \), Eq.~(\ref{eq:Lz_2}) can be rewritten as:
\begin{equation}
L_z = \frac{1}{2} \cdot \frac{\gamma m_0 v_\perp^2}{\omega_{ce}} = \frac{U}{\omega_{ce}},
\end{equation}
where \(\omega_{ce} = \dfrac{eB}{m_0 \gamma} = \dfrac{\omega_0}{\gamma}\) and \(U = \dfrac{1}{2} \gamma m_0 v_\perp^2\).
Here, \( m_0 \) is the electron rest mass, \( \gamma \) is the Lorentz factor, and \( \omega_0 \) is the electron cyclotron frequency in the rest frame (\( here we choose \omega_0 > 0 \)). The conservation of angular momentum in the \( z \)-direction is expressed as
\[
L_{z2} + m\hbar = L_{z1}.
\]
The variation in the angular momentum of the electron along the \( z \)-axis is given by:
\begin{equation}
\Delta L_{21} = L_{z2} - L_{z1} = \frac{U_2 - U_1}{\omega_{ce}} = -m\hbar \label{eq:DeltaL21}
\end{equation}
Here, \( m \) is the quantum number of the photon's angular momentum in the \( z \)-direction. The internal energy change is given by \( \Delta U_{21} = U_2 - U_1 \). With Eq.~(\ref{eq:DeltaL21}), it can be transformed as:
\begin{equation}
\Delta U_{21}=-m \hbar \omega_{ce}  \label{eq:DeltaU21}
\end{equation}
According to the Eq.~(\ref{eq:DeltaU00})  and Eq.~(\ref{eq:DeltaU21}), the change in electron energy  could be presented as 
\begin{equation}
\hbar \vec{k} \cdot \vec{v} = \hbar \omega - m \hbar \omega_{ce} \label{eq:EnergyResonant}
\end{equation}
This result is consistent with previous findings~\cite{tamm1959general, frank1960optics, nezlin1976negative, coppi1976slide, frolov1986excitation, ginzburg1996radiation}. Here, \( \hbar \vec{k} \cdot \vec{v} \) represents the loss of kinetic energy \( \Delta T_{12} \), \( \hbar \omega \) represents the energy of the photon, and \( -m \hbar \omega_{ce} \) represents the change in the electron gyrokinetic energy \( \Delta U_{21} \) (the internal energy change). The ratio between the internal energy change \( \Delta U_{21} \) and the kinetic energy change \( \Delta T_{21} \) can be expressed as
\begin{equation}
\frac{\Delta U_{21}}{\Delta T_{21}} = \frac{m \hbar \omega_{ce}}{\hbar \vec{k} \cdot \vec{v}}  \label{eq:DU21DT21}
\end{equation}
 This results is a critical criterion to compare with the classical dynamic simulation in the section 2. It is also proved based on classical theory in the Appendix.
After simpifying the Eq.~(\ref{eq:EnergyResonant}), we finally have the classical wave-particle resonant condition 
\begin{equation}
\omega = k_z v_z + m \omega_{ce}
\end{equation}
The variable \( m \) represents the quantum number associated with the angular momentum of the photon. Since a photon possesses both orbital angular momentum (\( l\hbar\), where \(l = 0,\pm1,\pm2,\pm3,... \)) and intrinsic spin angular momentum (\( s\hbar \), where \( s = \pm 1 \))~\cite{arnaut2000orbital}, the total angular momentum can be expressed as \( m\hbar = l\hbar + s\hbar \).

@@

\section{Classical dynamic simulation of ADR}\label{sec:level3}
The ADE process has been analyzed based on quantum theory, demonstrating that the angular momentum of the emitting photon determines the resonance condition.  These characteristics will be tested through the interaction of EM wave and the electron during ADR and NDR, and the energy transfer ratio can also be verified through numerical simulations.
\subsection{Numerical simulation setup}
To analyze the resonant process from the perspective of classical dynamics and to provide a direct comparison between quantum and classical dynamic results, the following scenario is considered: A uniform magnetic field \( \vec{B}_0 \) is applied along the \( z \)-direction. An electrostatic field \( \vec{E}_0 \), oriented in the opposite direction to \( \vec{B}_0 \) (as illustrated in Fig.~\ref{fig:Setup}), is used to accelerate the electron. 
\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{Figure4.eps}% Here is how to import EPS art
\caption{\label{fig:Setup}The uniform static magnetic field is set along the z axis, the electrostatic field $E_0$ is oriented opposite to the $B_0$ field, and the wavevector $k$ is aligned parallel to the $B_0$ field.}
\end{figure}
We consider the interaction between an electron entering the system with velocity \( v_z \), parallel to the magnetic field \( B_0 = B_z \), and a linearly or circularly polarized transverse electromagnetic (TEM) wave propagating in a homogeneous dielectric medium with a refractive index \( n > 1 \).

@@

\subsection{Validation of energy transfer ratio  }

@@

The Anomalous Doppler Resonance begins to emerge when the time reaches \( 113 \tau_{ce} \), where \( \omega_{\text{ADE}} = \omega \) as shown in Fig.~\ref{fig:kinetic_evolution}(a). At this point, the parallel velocity begins to scatter into the perpendicular direction, evident from the decrease in \( \Delta v_z \) and the increase in \( v_{\perp} \) as seen in Fig.~\ref{fig:kinetic_evolution}(c) and Fig.~\ref{fig:kinetic_evolution}(d). During the resonant period, the changes in parallel kinetic and gyro-kinetic energies caused by the electromagnetic wave are calculated as \( \Delta T_{21} = \Delta E_{||\text{emw}} \approx -96.2 \times 10^{-5} \, \text{eV} \) and \( \Delta E_{\perp} \approx 39.3 \times 10^{-5} \, \text{eV} \). The energy transfer ratio is \( \frac{\Delta U_{21}}{\Delta T_{21}} \approx -0.408 \). According to quantum theory, the change ratio of \( \Delta U_{21}/\Delta T_{21} = -\hbar \omega_{ce}/\hbar \vec{k} \cdot \vec{v} = -0.3908 \), where \( \omega_{ce} \approx 3.51 \times 10^9 \, \text{s}^{-1} \), and \( k = 10^5 \, \text{m}^{-1} \), \( v_z = 90 \, \text{km/s} \). The quantum theory results are in good agreement with the numerical calculations. The energy change ratio is also derived in the Appendix, based on classical theory.
\subsection{Validation of the relationship with wave angular momentum. }
\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{Figure6.eps}% Here is how to import EPS art
\caption{Velocity evolution caused by induced wave with linear, right-circular and left-circular polarization. (a) The cyclotron velocity $v_\perp$ .(b) The change of parallel velocity caused by the electromagnetic wave.}
    \label{fig:AngularMomentum}
\end{figure}

@@

\section{Discussion }\label{sec:Discussion}
Based on the momentum and angular momentum conservation analysis, Let's analyze the case where $\vec{k}$ is oriented opposite to $v_{\parallel}$(or $\vec{B_0}$). In this case, if a cyclotron electron emits a photon with left-hand circular polarization and momentum $-\hbar\vec{k}$, where the angular momentum carried by photon is $\hbar$, then after the emission, the change in internal energy is $\Delta U = -\hbar\omega_{ce}<0$, and the change in translational kinetic energy $\Delta T = \hbar k v_{\parallel}>0$. However, if the emitting photon have right-circular polarization and momentum $-\hbar\vec{k}$, the change of internal energy becomes $\Delta U = \hbar\omega_{ce}>0$, while the translational kinetic energy still is $\Delta T = \hbar k v_{\parallel}>0$. This would violate the conservation of energy, as it is not possible for an electron to emit a photon while simultaneously increasing its total energy. Consequently, for a plane electromagnetic wave, only the left-circularly polarized component can resonate with an electron moving opposite to $v_{\parallel}$ (or $\vec{B_0}$). 
%Based on momentum and angular momentum conservation analysis, we examine the case where $\vec{k}$ is oriented opposite to $\vec{v}_{\parallel}$ (or $\vec{B_0}$). 
%\begin{itemize}
%    \item \textbf{Left-hand circular polarization case}: When a cyclotron electron emits a photon with:
%
%    \begin{itemize}
%        \item Left-hand circular polarization ($\sigma^-$)
%        \item Momentum $-\hbar\vec{k}$
%        \item Angular momentum $+\hbar$
%    \end{itemize}
%    the resulting energy changes are:
%    \begin{align}
%        \Delta U &= -\hbar\omega_{ce} < 0 \quad \text{(decrease in internal energy)} \\
%        \Delta T &= +\hbar k v_{\parallel} > 0 \quad \text{(increase in translational energy)}
%    \end{align}
%
%    \item \textbf{Right-hand circular polarization case}: If the emitted photon had:
%    \begin{itemize}
%        \item Right-hand polarization ($\sigma^+$)
%        \item Momentum $-\hbar\vec{k}$
%        \item Angular momentum $-\hbar$
%    \end{itemize}
%    the energy changes would instead be:
%    \begin{align}
%        \Delta U &= +\hbar\omega_{ce} > 0 \quad \text{(increase in internal energy)} \\
%        \Delta T &= +\hbar k v_{\parallel} > 0 \quad \text{(increase in translational energy)}
%    \end{align}
%\end{itemize}

@@

\section{Conclusion}\label{sec:Conclusion}
This paper presents a simple yet effective method for analyzing the resonant processes associated with the Normal Doppler Effect (NDE) and Anomalous Doppler Effect (ADE). By combining quantum theory with angular momentum conservation analysis, it is shown that the parameter \( m \) in the resonance condition  
\(
\omega = \vec{k} \cdot \vec{v} + m\omega_{ce}
\)
is directly associated with the angular momentum of the resonant wave. Numerical simulations based on the Volume Preserving Algorithm (VPA) further support the quantum results, confirming both the angular momentum correspondence of \( m \) and the energy transfer characteristics. In future work, the interaction between electron energy transformation and helicon waves will be investigated within a plasma environment, aiming to provide deeper insights into applications such as plasma heating and runaway electron suppression.
\section{Acknowledgements}
This work is supported by National Magnetic Confinement Fusion Energy Program of China under Contract No. 2019YFE03020001
%\addcontentsline{toc}{chapter}{Appendix A: Appendix section heading}
\section*{Appendix A:Classical Analysis of Anomalous Doppler Resonance}
Neglecting the static electric field and relativistic effect , we provide a brief derivation of the energy transformation process based on classical dynamical equations:
\begin{align}
m_e \frac{d\vec{v}_\parallel}{dt} &= -e(\vec{v}_\perp \times \vec{B}_\perp) \label{eq:19} \\
m_e \frac{d\vec{v}_\perp}{dt} &= -e(\vec{v}_\perp \times \vec{B}_0 + \vec{v}_\parallel \times \vec{B}_\perp + \vec{v}_\perp \times \vec{B}_0) \label{eq:20}
\end{align}

@@

%\subsection*{5. References}
\bibliography{aipsamp_ADE}

>>>>

%=================================================================================================%
% This is a template designed for Chin. Phys. B (Dated 12 November 2014)
% Only one step to compile: PDFTeXify
%=================================================================================================%
\documentclass{cpbtex3}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\usepackage{authblk}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fontspec}
\usepackage{mathptmx}
%\usepackage{unicode-math}  
%\usepackage[backend=biber]{biblatex}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage{titlesec}      % For customizing section titles
% ===== 1. Small font for affiliations =====
\renewcommand{\Affilfont}{\small} % Set affiliation font size to small

@@

%\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{etoolbox}
\usepackage{microtype} 
\usepackage{caption}
\usepackage{hyperref}
\setmainfont{Times New Roman}
\captionsetup[figure]{labelfont=bf, name=Fig., labelsep=period}

@@

\begin{abstract}
%A quantum model incorporating angular momentum conservation is developed to analyze the Normal and Anomalous Doppler Effects, demonstrating that the resonance condition is strongly influenced by the angular momentum of the wave. The resonance condition involving wave angular momentum is examined numerically, and the energy exchange ratio between the electron's parallel and gyro-kinetic motion during resonance with the electromagnetic wave is simulated, exhibiting strong agreement with quantum theoretical predictions.
The fundamental physics of anomalous and normal doppler resonances between electron and electromagnetic waves is analyzed using a  quantum model incorporating angular momentum conservation. This work extends prior theory by explicitly linking the resonant integer m to the EM wave's angular momentum quantum number. Numerical simulations based on the Volume Preserving Algorithm (VPA) confirm this relationship. Furthermore, a direct comparison of the energy transfer ratio from translation energy to gyrokinetic energy during resonance between classical dynamics and quantum results is presented and verified numerically.
\end{abstract}

@@

\section{ Introduction}
The Anomalous Doppler Effect (ADE) \cite{tamm1959general,frank1960optics,ginzburg1960certain,shustin1971transformation}, in which the observed frequency shift behaves contrary to the conventional Doppler Effect under specific conditions, was first theoretically predicted by Soviet physicist Vitaly L. Ginzburg \cite{ginzburg1960certain}. This phenomenon arises when a system moves with a velocity exceeding the phase velocity of light in the medium, transferring its translational kinetic energy into internal energy while emitting radiation. A notable example, discussed by Frank in his 1958 Nobel lecture \cite{frank1960optics}, shows that radiation emission does not occur through the typical transition from an excited state to a lower energy state. Instead, it proceeds from a lower to a higher energy state, powered by the system's translational kinetic energy. This counterintuitive prediction has attracted considerable attention and has inspired extensive research \cite{nezlin1976negative,santini1984anomalous,kho1988slow,wang2016multi,guo2018control,liu2018role,shi2018superlight,filatov2021role}.

@@

The remainder of this paper is organized as follows. Section~\ref{Quantum}~~~~~develops the quantum theoretical framework incorporating angular momentum conservation. Section~\ref{sec:level3}~~~~ presents our numerical approach, detailing the simulation setup, analyzing the time evolution of electron velocity and kinetic energy, investigating the resonant conditions with wave angular momentum, and examining the energy transfer ratio and polarization characteristics. Section~\ref{sec:Discussion}~~~ provides a comprehensive discussion of the key findings and their physical implications. Finally, Section~\ref{sec:Conclusion}~~~ summarizes the principal conclusions and outlines potential directions for future research.

\section{ Quantum analysis of ADE}\label{Quantum}
%We begin with the quantum theory proposed by V.L. Ginzburg\cite{ginzburg2005radiation}based on the energy-momentum conservation, and then incorporate  angular momentum conservation to illustrate the relationship of wave’s angular momentum and Landau level n under the resonant condition $\omega = \vec{k}\cdot \vec{v}+m \omega_{ce}$, where $\omega$ is wave’s angular frequency, $\vec{k}$ represents the wave vector,  $\vec{v}$ means the velocity of electron and $ \omega_{ce}$ is the electron cyclotron angular frequency in static magnetic field, $ m =0,±1,±2,…  $is the quantum number of the Landau levels\cite{coppi1976slide}.

@@

The $z$-component of the orbital angular momentum operator can be expressed in spherical coordinates as:
\begin{equation}
\hat{L}_z = -i\hbar\frac{\partial}{\partial\phi}  \label{eq:Lz}
\end{equation}
Combining Eq.~(\ref{eq:psi}) with Eq.~(\ref{eq:Lz}), we have 
\begin{equation}
-i\hbar \frac{\partial}{\partial \phi} \Psi = (p_\phi - eA_\phi) r \Psi
\end{equation}
As a result, the eigenvalue of  $L_z $can be expressed as
\begin{equation}
L_z = (p_\phi - e A_\phi) r  \label{eq:Lz_2}
\end{equation}
With \( p_\phi = \gamma m_e v_\perp \), \( A_\phi = \dfrac{r B_0}{2} \), and \( r = \dfrac{\gamma m_0 v_\perp}{B_0 e} \), Eq.~(\ref{eq:Lz_2}) can be rewritten as:
\begin{equation}
L_z = \frac{1}{2} \cdot \frac{\gamma m_0 v_\perp^2}{\omega_{ce}} = \frac{U}{\omega_{ce}},
\end{equation}
where \(\omega_{ce} = \dfrac{eB}{m_0 \gamma} = \dfrac{\omega_0}{\gamma}\) and \(U = \dfrac{1}{2} \gamma m_0 v_\perp^2\).
Here, \( m_0 \) is the electron rest mass, \( \gamma \) is the Lorentz factor, and \( \omega_0 \) is the electron cyclotron frequency in the rest frame (here we choose \( \omega_0 > 0 \)). The conservation of angular momentum in the \( z \)-direction is expressed as
\[
L_{z2} + m\hbar = L_{z1}.
\]
The variation in the angular momentum of the electron along the \( z \)-axis is given by:
\begin{equation}
\Delta L_{21} = L_{z2} - L_{z1} = \frac{U_2 - U_1}{\omega_{ce}} = -m\hbar \label{eq:DeltaL21}
\end{equation}
Here, \( m \) is the quantum number of the photon's angular momentum in the \( z \)-direction. The internal energy change is given by \( \Delta U_{21} = U_2 - U_1 \). With Eq.~(\ref{eq:DeltaL21}), it can be transformed as:
\begin{equation}
\Delta U_{21}=-m \hbar \omega_{ce}  \label{eq:DeltaU21}
\end{equation}
According to the Eq.~(\ref{eq:DeltaU00})  and Eq.~(\ref{eq:DeltaU21}), the change in electron energy  could be presented as 
\begin{equation}
\hbar \vec{k} \cdot \vec{v} = \hbar \omega - m \hbar \omega_{ce} \label{eq:EnergyResonant}
\end{equation}
This result is consistent with previous findings~\cite{tamm1959general, frank1960optics, nezlin1976negative, coppi1976slide, frolov1986excitation, ginzburg1996radiation}. Here, \( \hbar \vec{k} \cdot \vec{v} \) represents the loss of kinetic energy \( \Delta T_{12} \), \( \hbar \omega \) represents the energy of the photon, and \( -m \hbar \omega_{ce} \) represents the change in the electron gyrokinetic energy \( \Delta U_{21} \) (the internal energy change). The ratio between the internal energy change \( \Delta U_{21} \) and the kinetic energy change \( \Delta T_{21} \) can be expressed as
\begin{equation}
\frac{\Delta U_{21}}{\Delta T_{21}} = \frac{m \hbar \omega_{ce}}{\hbar \vec{k} \cdot \vec{v}}  \label{eq:DU21DT21}
\end{equation}
 This results is a critical criterion to compare with the classical dynamic simulation in the section 2. It is also proved based on classical theory in the Appendix.
After simpifying the Eq.~(\ref{eq:EnergyResonant}), we finally have the classical wave-particle resonant condition 
\begin{equation}
\omega = k_z v_z + m \omega_{ce}
\end{equation}
The variable \( m \) represents the quantum number associated with the angular momentum of the photon. Since a photon possesses both orbital angular momentum (\( l\hbar\), where \(l = 0,\pm1,\pm2,\pm3,... \)) and intrinsic spin angular momentum (\( s\hbar \), where \( s = \pm 1 \))~\cite{arnaut2000orbital}, the total angular momentum can be expressed as \( m\hbar = l\hbar + s\hbar \).

@@

\section{ Classical dynamic simulation of ADR}\label{sec:level3}
The ADE process has been analyzed based on quantum theory, demonstrating that the angular momentum of the emitting photon determines the resonance condition.  These characteristics will be tested through the interaction of EM wave and the electron during ADR and NDR, and the energy transfer ratio can also be verified through numerical simulations.
\subsection{ Numerical simulation setup}
To analyze the resonant process from the perspective of classical dynamics and to provide a direct comparison between quantum and classical dynamic results, the following scenario is considered: A uniform magnetic field \( \vec{B}_0 \) is applied along the \( z \)-direction. An electrostatic field \( \vec{E}_0 \), oriented in the opposite direction to \( \vec{B}_0 \) (as illustrated in Fig.~\ref{fig:Setup}), is used to accelerate the electron. 
\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{Figure4.eps}% Here is how to import EPS art
\caption{\label{fig:Setup}The uniform static magnetic field is set along the z axis, the electrostatic field $E_0$ is oriented opposite to the $B_0$ field, and the wavevector $k$ is aligned parallel to the $B_0$ field.}
\end{figure}
We consider the interaction between an electron entering the system with velocity \( v_z \), parallel to the magnetic field \( B_0 = B_z \), and a linearly or circularly polarized transverse electromagnetic (TEM) wave propagating in a homogeneous dielectric medium with a refractive index \( n > 1 \).

@@

\subsection{ Validation of energy transfer ratio  }

@@

The Anomalous Doppler Resonance begins to emerge when the time reaches \( 113 \tau_{ce} \), where \( \omega_{\text{ADE}} = \omega \) as shown in Fig.~\ref{fig:kinetic_evolution}(a). At this point, the parallel velocity begins to scatter into the perpendicular direction, evident from the decrease in \( \Delta v_z \) and the increase in \( v_{\perp} \) as seen in Fig.~\ref{fig:kinetic_evolution}(c) and Fig.~\ref{fig:kinetic_evolution}(d). During the resonant period, the changes in parallel kinetic and gyro-kinetic energies caused by the electromagnetic wave are calculated as \( \Delta T_{21} = \Delta E_{||\text{emw}} \approx -96.2 \times 10^{-5} \, \text{eV} \) and \( \Delta E_{\perp} \approx 39.3 \times 10^{-5} \, \text{eV} \). The energy transfer ratio is \( \frac{\Delta U_{21}}{\Delta T_{21}} \approx -0.408 \). According to quantum theory, the change ratio of \( \Delta U_{21}/\Delta T_{21} = -\hbar \omega_{ce}/\hbar \vec{k} \cdot \vec{v} = -0.3908 \), where \( \omega_{ce} \approx 3.51 \times 10^9 \, \text{s}^{-1} \), and \( k = 10^5 \, \text{m}^{-1} \), \( v_z = 90 \, \text{km/s} \). The quantum theory results are in good agreement with the numerical calculations. The energy change ratio is also derived in the Appendix, based on classical theory.
\subsection{ Validation of the relationship with wave angular momentum. }
\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{Figure6.eps}% Here is how to import EPS art
\caption{Velocity evolution caused by induced wave with linear, right-circular and left-circular polarization. (a) The cyclotron velocity $v_\perp$ .(b) The change of parallel velocity caused by the electromagnetic wave.}
    \label{fig:AngularMomentum}
\end{figure}

@@

\section{ Discussion }\label{sec:Discussion}
Based on the momentum and angular momentum conservation analysis, Let's analyze the case where $\vec{k}$ is oriented opposite to $v_{\parallel}$(or $\vec{B_0}$). In this case, if a cyclotron electron emits a photon with left-hand circular polarization and momentum $-\hbar\vec{k}$, where the angular momentum carried by photon is $\hbar$, then after the emission, the change in internal energy is $\Delta U = -\hbar\omega_{ce}<0$, and the change in translational kinetic energy $\Delta T = \hbar k v_{\parallel}>0$. However, if the emitting photon have right-circular polarization and momentum $-\hbar\vec{k}$, the change of internal energy becomes $\Delta U = \hbar\omega_{ce}>0$, while the translational kinetic energy still is $\Delta T = \hbar k v_{\parallel}>0$. This would violate the conservation of energy, as it is not possible for an electron to emit a photon while simultaneously increasing its total energy. Consequently, for a plane electromagnetic wave, only the left-circularly polarized component can resonate with an electron moving opposite to $v_{\parallel}$ (or $\vec{B_0}$). 
%Based on momentum and angular momentum conservation analysis, we examine the case where $\vec{k}$ is oriented opposite to $\vec{v}_{\parallel}$ (or $\vec{B_0}$). 
%\begin{itemize}
%    \item \textbf{Left-hand circular polarization case}: When a cyclotron electron emits a photon with:
%
%    \begin{itemize}
%        \item Left-hand circular polarization ($\sigma^-$)
%        \item Momentum $-\hbar\vec{k}$
%        \item Angular momentum $+\hbar$
%    \end{itemize}
%    the resulting energy changes are:
%    \begin{align}
%        \Delta U &= -\hbar\omega_{ce} < 0 \quad \text{(decrease in internal energy)} \\
%        \Delta T &= +\hbar k v_{\parallel} > 0 \quad \text{(increase in translational energy)}
%    \end{align}
%
%    \item \textbf{Right-hand circular polarization case}: If the emitted photon had:
%    \begin{itemize}
%        \item Right-hand polarization ($\sigma^+$)
%        \item Momentum $-\hbar\vec{k}$
%        \item Angular momentum $-\hbar$
%    \end{itemize}
%    the energy changes would instead be:
%    \begin{align}
%        \Delta U &= +\hbar\omega_{ce} > 0 \quad \text{(increase in internal energy)} \\
%        \Delta T &= +\hbar k v_{\parallel} > 0 \quad \text{(increase in translational energy)}
%    \end{align}
%\end{itemize}

@@

\section{ Conclusion}\label{sec:Conclusion}
This paper presents a simple yet effective method for analyzing the resonant processes associated with the Normal Doppler Effect (NDE) and Anomalous Doppler Effect (ADE). By combining quantum theory with angular momentum conservation analysis, it is shown that the parameter \( m \) in the resonance condition  
\(
\omega = \vec{k} \cdot \vec{v} + m\omega_{ce}
\)
is directly associated with the angular momentum of the resonant wave. Numerical simulations based on the Volume Preserving Algorithm (VPA) further support the quantum results, confirming both the angular momentum correspondence of \( m \) and the energy transfer characteristics. In future work, the interaction between electron energy transformation and helicon waves will be investigated within a plasma environment, aiming to provide deeper insights into applications such as plasma heating\cite{zhao2022plasma} and runaway electron suppression.
\section*{ Acknowledgements}
This work is supported by National Magnetic Confinement Fusion Energy Program of China under Contract No. 2019YFE03020001
%\addcontentsline{toc}{chapter}{Appendix A: Appendix section heading}
\section*{Appendix A: Classical Analysis of Anomalous Doppler Resonance}
Neglecting the static electric field and relativistic effect , we provide a brief derivation of the energy transformation process based on classical dynamical equations:
\begin{align}
m_e \frac{d\vec{v}_\parallel}{dt} &= -e(\vec{v}_\perp \times \vec{B}_\perp) \label{eq:19} \\
m_e \frac{d\vec{v}_\perp}{dt} &= -e(\vec{v}_\perp \times \vec{B}_0 + \vec{v}_\parallel \times \vec{B}_\perp + \vec{v}_\perp \times \vec{B}_0) \label{eq:20}
\end{align}

@@

%\subsection*{5. References}
\begin{thebibliography}{99}\footnotesize
\itemsep=-3pt plus.2pt minus.2pt
\bibitem{tamm1959general} Tamm I E \href{https://doi.org/10.1007/978-3-642-74626-0_4}{1959 {\em Nobel Lectures} {\bf 18} 122}
\bibitem{frank1960optics} Frank I M \href{https://doi.org/10.1126/science.131.3402.702}{1960 {\em Science} {\bf 131} 702}
\bibitem{kiang2008angular} Kiang D and Young K \href{https://doi.org/10.1119/1.2957885}{2008 {\em Am. J. Phys.} {\bf 76} 1012}
\bibitem{ginzburg1960certain} Ginzburg V L \href{https://doi.org/10.1070/PU1960v002n06ABEH003185}{1960 {\em Sov. Phys. Usp.} {\bf 2} 874}
\bibitem{shustin1971transformation} Shustin E G, Popovich P and Kharchenko I F \href{http://83.149.229.155/cgi-bin/dn/e_032_03_0358.pdf}{1971 {\em Sov. Phys. JETP} {\bf 59} 657}
\bibitem{nezlin1976negative} Nezlin M V \href{https://www.ufn.ru/ufn76/ufn76_11/ufn7611f.pdf}{1976 {\em Sov. Phys. Usp.} {\bf 19} 946}
\bibitem{santini1984anomalous} Santini F, Barbato E and De Marco F \href{https://doi.org/10.1103/PhysRevLett.52.1300}{1984 {\em Phys. Rev. Lett.} {\bf 52} 1300}
\bibitem{kho1988slow} Kho T H and Lin A T \href{https://doi.org/10.1103/PhysRevA.38.2883}{1988 {\em Phys. Rev. A} {\bf 38} 2883}
\bibitem{liu2016collisionless} Liu J, Wang Y and Qin H 2016 \href{https://doi.org/10.1088/0029-5515/56/6/064002}{{\em Nucl. Fusion} {\bf 56} 064002}
\bibitem{wang2016multi} Wang Y, Qin H and Liu J \href{https://doi.org/10.1063/1.4953608}{2016 {\em Phys. Plasmas} {\bf 23} 062505}
\bibitem{guo2018control} Guo Z, McDevitt C J and Tang X Z \href{https://doi.org/10.1063/1.5019381}{2018 {\em Phys. Plasmas} {\bf 25} 032504}
\bibitem{liu2018role} Liu C, Hirvijoki E and Fu G Y \href{https://doi.org/10.1103/PhysRevLett.120.265001}{2018 {\em Phys. Rev. Lett.} {\bf 120} 265001}
\bibitem{shi2018superlight} Shi X, Lin X and Kaminer I \href{https://doi.org/10.1038/s41567-018-0209-6}{2018 {\em Nat. Phys.} {\bf 14} 1001}
\bibitem{filatov2021role} Filatov L V and Melnikov V F \href{https://doi.org/10.1134/S0016793221080077}{2021 {\em Geomagn. Aeron.} {\bf 61} 1183}
\bibitem{artsimovich1967thermal} Artsimovich L A, Bobrovskii G A and Mirnov S V \href{https://doi.org/10.1007/BF01116249}{1967 {\em Sov. At. Energy} {\bf 22} 325}
\bibitem{kadomtsev1968electric} Kadomtsev B B and Pogutse O P \href{http://www.jetp.ras.ru/cgi-bin/dn/e_026_06_1146.pdf}{1968 {\em Sov. Phys. JETP} {\bf 26} 1146}
\bibitem{spong2018first} Spong D A, Heidbrink W W and Paz-Soldan C \href{https://doi.org/10.1103/PhysRevLett.120.155002}{2018 {\em Phys. Rev. Lett.} {\bf 120} 155002}
\bibitem{liu2019intense} Liu Y, Zhou T and Hu Y \href{https://doi.org/10.1088/1741-4326/ab3541}{2019 {\em Nucl. Fusion} {\bf 59} 106024}
\bibitem{gorozhanin1997waves} Gorozhanin D V, Ivanov B I and Khoruzhiy V M \href{https://www.osti.gov/etdeweb/biblio/576289}{1997 {\em Waves excitation at anomalous Doppler effect for various electron beam energies,} Dec 31, 1997, Japan, p. 402}
\bibitem{sajjad2007runaway} Sajjad S \href{https://doi.org/10.1088/0256-307X/24/11/048}{2007 {\em Chin. Phys. Lett.} {\bf 24} 3195} 
\bibitem{castejon2003particle} Castejon F and Eguilior S \href{https://inis.iaea.org/records/0t7nf-dc366}{2003 \textit{Particle Dynamics under Quasi-linear Interaction with Electromagnetic Waves} (Madrid: Centro de Investigaciones Energeticas) p. 4}
